---
title: "housing prices data memo"
author: "James(Changhwan) Han (3923257)"
date: "5/31/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading libraries
```{r, warning = FALSE}
library(tidymodels)
library(tidyverse)
```

# Dataset
```{r}
df <- read_csv("housing.csv")

colSums(is.na(df))
head(df)
```


# An overview of my dataset
1.What does it include? \
2.Where and how will you be obtaining it? Include the link and source. \
3.About how many observations? How many predictors? \
4.What types of variables will you be working with? \
5.Is there any missing data? About how much? Do you have an idea for how to handle it? \
\

1. The dataset includes median house prices for California districts derived from the 1990 census. \
2. I obtained this dataset from Kaggle, https://www.kaggle.com/datasets/camnugent/california-housing-prices \
3,4. There are 20640 observations and 9 predictors; longitude, latitude, housing_median_age, total_rooms, total_bedrooms, population, households, median_income, and ocean_proximity. \
5. Yes, there are 207 missing values in total_bedrooms column. I'm going to fill in missing values with median instead of mean because it is less influenced by extreme outliers.

# An overview of your research question
1.What variable(s) are you interested in predicting? What question(s) are you interested in answering? \
2.Name your response/outcome variable(s) and briefly describe it/them. \
3.Will these questions be best answered with a classification or regression approach? \
4.Which predictors do you think will be especially useful? \
5.Is the goal of your model descriptive, predictive, inferential, or a combination? Explain. \
\

1.

# Your proposed project timeline
1.When do you plan on having your data set loaded, beginning your exploratory data analysis, etc? \
2.Provide a general timeline for the rest of the quarter. \
\

# Any questions or concerns
1.Are there any problems or difficult aspects of the project you anticipate? \
2.Any specific questions you have for me/the instructional team?\
\
